Deriving a precise Newtonian equation for the time it takes two separated bodies in an isolated system to collide due to the gravitational force

### 2022-10-30 paper/draft.tex
cleanup

so that we finally have the solution to this section of the problem

@@

We have the solution to our integral, so we can now just substitute it in (\ref{eq:primary_solution}) and solve the definite integral for $\Delta T$ to get our final equation:

>>>>

and we then finally have the solution to this section of the problem

@@

Now that we have the solution to our integral, we can just substitute it in (\ref{eq:primary_solution}) and solve the definite integral for $\Delta T$ to get our final equation:
